### 2008-11-09 anal-plot.tkz.tex
Moved plot grid to separate file

% `\input{anal-plot.tkz.tex}` in your tikzpicture to use this. Parent
% picture must define `axis` and `grid` styles

\coordinate[] (O) at (0,0) {};

% cartesian coordinates
\draw [axis,->] ($ (O) - (0,1.8) $)--($ (O) + (0,0.5) $) node[label=left:$y$] {};
\draw [axis,->] (O)--($ (O) + (1.5,0) $) node[label=above:$x$] {};

% axis marks
\draw[] (0pt,-1pt) -- (0pt,1pt);
\node[label=above left:$0$] at (O) {};

\foreach \x/\xtext in {.5/\frac{1}{2}, 1}
{\begin{scope}
    \draw[xshift=\x cm,grid] (0,0)--(0,-1.65);
    \draw[xshift=\x cm] (0pt,-1pt) -- (0pt,1pt) node[above] {$\xtext$};
  \end{scope}}

\foreach \y/\ytext in {-1.5/-\frac{3}{2}, -1, -.5/-\frac{1}{2}, 0/}
{\begin{scope}
    \draw[yshift=\y cm,grid] (0,0)--(1.2,0);
    \draw[yshift=\y cm] (1pt,0pt)--(-1pt,0pt) node[left] {$\ytext$};
  \end{scope}}