### 2008-11-10 series-plot.tkz.tex
Added Maxima program to build and plot series, included plot in the paper

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=3,
                      axis/.style={draw=gray,thin},
                      grid/.style={axis,dotted}]

    \input{anal-plot.tkz.tex}
    \draw plot[only marks, mark=*, mark size=.4] file{series.mac.out};
  \end{tikzpicture}
  \label{fig:series-plot}
  \caption{Сравнение точного решения \eqref{eq:anal-solution} и
    решения в виде ряда \eqref{eq:gs-solution}}
\end{figure}