### 2008-11-20 anal-plot.tkz.tex
Using `grid` operation instead of cycles

% `\input{anal-plot.tkz.tex}` in your tikzpicture to use this. Parent
% picture must define `axis` and `grid` styles

\coordinate[] (O) at (0,0) {};

% grid
\draw[help lines, densely dashed] ($ (O) - (0,1.6) $) grid[xstep=.5,ystep=.5] ($ (O) + (1.1,0) $);

% cartesian coordinates
\draw [help lines,->] ($ (O) - (0,1.8) $)--($ (O) + (0,0.5) $) node[label={[black]left:$y$}] {};
\draw [help lines,->] (O)--($ (O) + (1.5,0) $) node[label={[black]above:$x$}] {};

% axis marks
\draw[] (0pt,-1pt) -- (0pt,1pt);
\node[label=above left:$0$] at (O) {};

\foreach \x/\xtext in {.5/\frac{1}{2}, 1}
{\begin{scope}
    \draw[xshift=\x cm] (0pt,-1pt) -- (0pt,1pt) node[above] {$\xtext$};
  \end{scope}}

\foreach \y/\ytext in {-1.5/-\frac{3}{2}, -1, -.5/-\frac{1}{2}, 0/}
{\begin{scope}
    \draw[yshift=\y cm] (1pt,0pt)--(-1pt,0pt) node[left] {$\ytext$};
  \end{scope}}

\draw[very thick, color=gray] plot[domain=-0.1:1.1] function{sinh(-1)*cos(x)/sin(1)};