### 2008-11-20 series-plot.tpl.tkz.tex

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=4]

    \input{anal-plot.tkz.tex}

    \draw plot[only marks, mark=*, mark size=.4] file{series-__N.mac.out};
  \end{tikzpicture}
  \caption{Сравнение точного решения \eqref{eq:anal-solution} и
    решения в виде ряда \eqref{eq:gs-solution} при количестве членов
    ряда $n=__N$}
  \label{fig:series-plot}
\end{figure}