### 2008-11-23 series-plot.tpl.tkz.tex

\input{axis-options.tkz}
\begin{figure}[htb]
  \centering
  \begin{tikzpicture}
    \begin{axis}
      \input{anal-plot.tkz.tex}

      \addplot[only marks,mark=*] file{series-__N.mac.out};
    \end{axis}
  \end{tikzpicture}
  \caption{Сравнение точного решения \eqref{eq:anal-solution} и
    решения в виде ряда \eqref{eq:gs-solution} при количестве членов
    ряда $n=__N$}
  \label{fig:series-plot}
\end{figure}