### 2008-11-23 series-plot.tpl.tkz.tex
Rich figure captions

\input{axis-options.tkz}
\begin{figure}[htb]
  \centering
  \begin{tikzpicture}
    \begin{axis}
      \input{anal-plot.tkz.tex}
      \label{plot:anal-by-series-__N}

      \addplot[smooth, mark=*] file{series-__N.mac.out};
      \label{plot:series-__N}
    \end{axis}
  \end{tikzpicture}
  \caption{Точное решение \ref{plot:anal-by-series-__N}
    \eqref{eq:anal-solution} и решение в виде ряда
    \ref{plot:series-__N} \eqref{eq:gs-solution} при количестве членов
    ряда $n=__N$}
  \label{fig:series-plot}
\end{figure}