### 2008-11-23 anal-plot.tkz.tex
Wider plotted range

% `\input{anal-plot.tkz.tex}` in your tikzpicture to use this

\addplot[very thick, color=gray] plot[domain=-0.2:1.2] function{sinh(-1)*cos(x)/sin(1)};